Document Classification

### 2018-11-01 DATA607/Project_4.Rmd
Modified Project_4.Rmd

@@

### Data Aquisition

@@

Now that the files have been aquired, they need to be decompressed.

@@

This model will classify only on the basis of the content.  The header information will not be taken into consideration.  In order to illustrate the process I will take the first message in the spam training set as an example.

```{r}
example_file <- spam$train[1]

get_email_contents <- function(file_name, path){
 full_path = paste0(path, file_name)
 con <- file(full_path)
 readLines(con)
}

```

### Split up Sentance

### Remove Punctuation and Stop Words

### Stemming

>>>>

```{r init, echo=FALSE, message=FALSE}
library(dplyr)
library(rmdformats)
library(kableExtra)

# A Prefix nulling hook.
# Taken from https://stackoverflow.com/questions/22524822/how-can-i-remove-the-prefix-index-indicator-1-in-knitr-output

# Make sure to keep the default for normal processing.
default_output_hook <- knitr::knit_hooks$get("output")

# Output hooks handle normal R console output.
knitr::knit_hooks$set(output = function(x, options) {

  comment <- knitr::opts_current$get("comment")
  if (is.na(comment)) comment <- ""
  can_null <- grepl( paste0( comment, "\\s*\\[\\d?\\]" ),
                     x, perl = TRUE)
  do_null <- isTRUE( knitr::opts_current$get("null_prefix") )
  if (can_null && do_null) {
    # By default R print output aligns at the right brace.
    align_index <- regexpr( "\\]", x )[1] - 1
    # Two cases: start or newline
    re <- paste0( "^.{", align_index, "}\\]")
    rep <- comment
    x <- gsub( re, rep,  x )
    re <- paste0( "\\\n.{", align_index, "}\\]")
    rep <- paste0( "\n", comment )
    x <- gsub( re, rep,  x )
    # I added this line
    x <- gsub( "##", "", x)
  }

  default_output_hook( x, options )
})

knitr::opts_template$set("kill_prefix" = list(comment = NA, null_prefix = TRUE))
```

@@

### Data Acquisition

@@

Now that the files have been acquired, they need to be decompressed.

@@

This model will classify only on the basis of the content.  The header information will not be taken into consideration.  In order to illustrate the process I will take the first message in the spam training set as an example.  Here's what the file looks like:

##### Table 2. Preview of Spam Email Message
```{r spam_preview, null_prefix=TRUE, echo=FALSE}
example_file <- spam$train[1]
full_path <- paste0("data/spam_2/", example_file)
con <- file(full_path)
print(readLines(con), quote = FALSE)
```

The message is split into two parts: the header and the body of the message.  Since we want to analyze the body of the email one observes it is seperated from the header by a blank line.  This will be how we will determine where the body of the message begins.

### Approach

In order to process a message body I will remove all punctuation

### Remove Punctuation

```{r get_message, message=FALSE}
library(dplyr)
library(tidytext)

stem_hunspell <- function(term) {
  # Taken from https://cran.r-project.org/web/packages/corpus/vignettes/stemmer.html
  # look up the term in the dictionary
  stems <- hunspell::hunspell_stem(term)[[1]]
  if (length(stems) == 0) { # if there are no stems, use the original term
    stem <- term
  } else { # if there are multiple stems, use the last one
    stem <- stems[[length(stems)]]
  }
  stem
}

get_message <- function(full_path){
  message <- ''
  header_finished <- FALSE
  # Open the file
  con <- file(full_path, blocking = FALSE)
  # Go line by line
  for(line in readLines(con)){
    # Order matters.  I don't want to lead with the blank line between the header
    if(header_finished){
      message <- paste(message, line)
    }
    # Look for the end of the header
    if(line == ""){
      header_finished <- TRUE
    }
  }
  # Close the connection to the file
  close(con)

  # Change text to lower case 
  message <- tolower(message)
  # Remove all punctuation
  message <- gsub("[[:punct:][:blank:]]+", " ", message)
  # Tokenize message
  words <- scan_tokenizer(message)
  # Remove stop words
  stop_words <- tm::stopwords()
  words <- words[!words %in% stop_words]
  # Stem words using hunspell
  words <- unlist(lapply(words, stem_hunspell))

  return(words)
}

full_path <- paste0("data/spam_2/", example_file)

bag_of_words <- get_message(full_path)
df <- data.frame(word = bag_of_words, count = c(1)) %>%
  group_by(word) %>%
  summarise(count = sum(count)) %>%
  ungroup() %>%
  mutate(file = example_file, type = "spam")
```

## TF-IDF Normalization
